PANNEURO_analysis

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd

>>>>

```{r nmsw col names}
nmsw.col.names <- dat.raw %>%
  select(
    starts_with("nmsw") & ends_with("numeric")
  ) %>% 
  colnames()
nmsw.col.names

```

```{r scoring NMSW}
dat.raw <- dat.raw %>% 
  mutate(nmsw.sum_score = 
           rowSums(select(.,nmsw.col.names), na.rm = FALSE)
           )

```

```{r}
nmsw.col.names <- dat.raw %>%
  select(
    starts_with("ess") & ends_with("numeric")
  ) %>% 
  colnames()
nmsw.col.names
```
```{r}
dat.raw <- dat.raw %>% 
  filter(ess.felt_excessively_sleepy_past_numeric == 1) %>%
  mutate(ess.sum_score = 
           rowSums(select(.,nmsw.col.names), na.rm = FALSE)
           )

```
